Archive Your Project

### 2025-07-09 archive.qmd
Fix typos
Introduced in 9e90838
Also cite overall software deposit guidance

The project folder is now ready to be deposited for long-term archival.
When considering an appropriate repository,
there are a few questions to ponder
[excerpt from @Jackson2018, with footnotes removed, licensed under [CC\ BY\ 4.0][cc-by]]:

@@

[re2data]: https://www.re3data.org/
[sw-heritage]: https://www.softwareheritage.org/
[zenodo]: https://zenodo.org/

@@

For further information, you may be interested in
[Software Deposit Guidance for Researchers](https://softwaresaved.github.io/software-deposit-guidance/).

>>>>

The project folder is now ready to be deposited for long-term archival.
When considering an appropriate repository,
there are a few questions to ponder
[excerpt from @Jackson2018Where, with footnotes removed, licensed under [CC\ BY\ 4.0][cc-by]]:

@@

[re3data]: https://www.re3data.org/
[sw-heritage]: https://www.softwareheritage.org/
[zenodo]: https://zenodo.org/

@@

For further information, you may be interested in
"Software Deposit Guidance for Researchers" [@Jackson2018Guidance].
